---
title: "Classification 2"
author: "Chris Okura"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
--


```{r setup, include=FALSE}
library(tidyverse)
library(tidymodels)
library(kknn)
library(glmnet)
library(discrim)
library(klaR)
```


# LDA

```{r, message = FALSE}
ins <- read_csv("https://www.dropbox.com/s/bocjjyo1ehr5auz/insurance.csv?dl=1")

ins <- ins %>%
  mutate(
    smoker = factor(smoker)
  ) %>%
  drop_na()
head(ins)
```


```{r set_mod}
lda_mod <- discrim_linear() %>%
  set_engine("MASS") %>%
  set_mode("classification")
```


```{r}
lda_fit_1 <- lda_mod %>%
  fit(smoker ~ charges, data = ins)

lda_fit_1$fit %>% summary()
```


```{r}
lda_fit_1 

preds <- lda_fit_1 %>% predict(ins)

ins <- ins %>%
  mutate(
    pred_smoker = preds$.pred_class
  )

ins %>%
  accuracy(truth = smoker,
           estimate = pred_smoker)
```


```{r}
lda_fit_2 <- lda_mod %>%
  fit(smoker ~ charges + age, data = ins)

lda_fit_2


preds2 <- lda_fit_2 %>% predict(ins)

ins <- ins %>%
  mutate(
    pred_smoker_fit_2 = preds2$.pred_class
  )

ins %>%
  accuracy(truth = smoker,
           estimate = pred_smoker_fit_2)
```


```{r}
lda_fit_2$fit$scaling
```

```{r, echo = FALSE}
ins %>%
  ggplot(aes(x = charges, y = age, color = smoker)) +
  geom_point()
```

```{r}
lda_fit_2

my_slope = lda_fit_2$fit$scaling[1]/(-1*lda_fit_2$fit$scaling[2])
```


```{r, echo = FALSE}

ins %>%
  ggplot(aes(x = charges, y = age, color = smoker)) +
  geom_point() +
  geom_abline(aes(slope = my_slope, intercept = 0))
```

#### Your turn:

Find the best LDA model to predict smoker status.



### Model Specifications

```{r}
knn_mod <- nearest_neighbor(neighbors = 5) %>%
  set_engine("kknn") %>%
  set_mode("classification")

logit_mod <- logistic_reg() %>%
  set_mode("classification") %>%
  set_engine("glm")

```

Model Recipes

```{r}
ins_rec_1 <- recipe(smoker ~ charges + age + bmi, data = ins)
ins_rec_2 <- recipe(smoker ~ charges + age + bmi + sex, data = ins)
ins_rec_3 <- recipe(smoker ~ charges + age + bmi + sex + region, data = ins)

```

Workflow
```{r}
ins_wflow_logit_1 <- workflow() %>%
  add_recipe(ins_rec_1) %>%
  add_model(logit_mod)

ins_wflow_logit_2 <- workflow() %>%
  add_recipe(ins_rec_2) %>%
  add_model(logit_mod)

ins_wflow_logit_3 <- workflow() %>%
  add_recipe(ins_rec_3) %>%
  add_model(logit_mod)

ins_wflow_knn_1 <- workflow() %>%
  add_recipe(ins_rec_1) %>%
  add_model(knn_mod)

ins_wflow_knn_2 <- workflow() %>%
  add_recipe(ins_rec_2) %>%
  add_model(knn_mod)

ins_wflow_knn_3 <- workflow() %>%
  add_recipe(ins_rec_3) %>%
  add_model(knn_mod)

```


### Cross Validation of Logistic Model 1
```{r}
ins_cvs <- vfold_cv(ins, v = 10)
log_1_cv <- logit_mod %>%
  fit_resamples(ins_rec_1, resamples = ins_cvs)
log_1_cv %>% collect_metrics()
```
### Cross Validation of Logistic Model 2
```{r}
log_2_cv <- logit_mod %>%
  fit_resamples(ins_rec_2, resamples = ins_cvs)
log_2_cv %>% collect_metrics()
```


### Cross Validation of Logistic Model 3
```{r}
log_3_cv <- logit_mod %>%
  fit_resamples(ins_rec_3, resamples = ins_cvs)
log_3_cv %>% collect_metrics()
```
### Cross Validation of KNN Model 1
```{r}
knn_1_cv <- knn_mod %>%
  fit_resamples(ins_rec_1, resamples = ins_cvs)
knn_1_cv %>% collect_metrics()
```

### Cross Validation of KNN Model 1
```{r}
knn_2_cv <- knn_mod %>%
  fit_resamples(ins_rec_2, resamples = ins_cvs)
knn_2_cv %>% collect_metrics()
```

### Cross Validation of KNN Model 1
```{r}
knn_3_cv <- knn_mod %>%
  fit_resamples(ins_rec_3, resamples = ins_cvs)
knn_3_cv %>% collect_metrics()
```

How does it compare to the Logistic Regression and KNN approaches?
The LDA performs a little bit worse in terms of accuracy compared to the KNN and logistic models. The highest performing model was KNN with n = 5 and explanatory variables charges, age, and bmi. 

### CHECKPOInT

# Quadratic Discriminant Analysis

#### Code from lecture:

```{r qda_mod}
qda_mod <- discrim_regularized(frac_common_cov = 0) %>% 
             set_engine('klaR') %>% 
             set_mode('classification')
```

```{r, echo = FALSE}
dat <- tibble(
  A = rnorm(100, 10, 5),
  B = rnorm(100, 15, 1)
) %>%
  pivot_longer(everything(),
               values_to = "val",
               names_to = "Class")

ggplot(dat, aes(x = val, fill = Class)) +
  geom_density(alpha = 0.5) +
  geom_vline(xintercept = 11)
```


```{r, echo = FALSE}
dat <- tibble(
  V1 = c(rnorm(100, 10, 5), rnorm(100, 37, 18)),
  V2 = c(rnorm(100, 15, 1), rnorm(100, 30, 9)),
  Class = factor(c(rep("A", 100), rep("B", 100)))
) 

dat %>%
  ggplot(aes(x = V1, y = V2, col = Class)) +
  geom_point()
```


```{r, echo = FALSE}
qda_wflow <- workflow() %>%
  add_recipe(recipe(Class ~ V1 + V2, data = dat)) %>%
  add_model(qda_mod) %>%
  fit(dat)

#qda_wflow %>%
#  horus::viz_decision_boundary(dat)
```

#### Your turn:

Find the best QDA model to predict smoker status.

```{r}

qda_mod1 <- discrim_regularized(frac_common_cov = 0) %>% 
             set_engine('klaR') %>% 
             set_mode('classification')

qda_wflow1 <- workflow() %>%
  add_recipe(recipe(smoker ~ charges + age + bmi + sex, data = ins)) %>%
  add_model(qda_mod1) %>%
  fit(ins)

qda_pred_class <- qda_wflow1 %>% predict(ins)

qda_test1 <- ins %>%
  mutate(
    pred_output = qda_pred_class$.pred_class
  ) 
 
qda_test1 %>%
  accuracy(truth = smoker,
           estimate = pred_output)

qda_mod2 <- discrim_regularized(frac_common_cov = 8) %>% 
             set_engine('klaR') %>% 
             set_mode('classification')

qda_wflow2 <- workflow() %>%
  add_recipe(recipe(smoker ~ charges + age + bmi + sex, data = ins)) %>%
  add_model(qda_mod2) %>%
  fit(ins)

qda_pred_class <- qda_wflow2 %>% predict(ins)

qda_test2 <- ins %>%
  mutate(
    pred_output = qda_pred_class$.pred_class
  ) 
 
qda_test2 %>%
  accuracy(truth = smoker,
           estimate = pred_output)

```



How does it compare to the LDA, Logistic Regression, and KNN approaches?
The 

# Metrics

https://yardstick.tidymodels.org/articles/metric-types.html



